### 2014-03-14 src/analysis.Rnw
update

\begin{figure*}[t]
<<op.all.3,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
dfd <- subset(df, !(strategy %in% c('op','opsel')) )
ggplot(dfd, aes(sd.reduction, mutant.reduction)) + geom_point(aes(shape=type, color=sqr)) + facet_wrap(~strategy) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
@
\label{fig:fullimgshape}
\end{figure*}
<<opsel>>=
stats.op <- subset(stats.rest, grepl('^(op|TSDL)', operator))
o.stats.sel.op <- subset(o.f(stats.op), select=sel.colnames)
r.stats.sel.op <- subset(r.f(stats.op), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^(op|TSDL)', operator))
colnames(o.stats.sel.op) <- new.colnames
colnames(r.stats.sel.op) <- new.colnames

o.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
r.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')

@@

#o.stats.sel.one$sampling  <- gsub('_.*','', o.stats.sel.one$operator)

@

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.op, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.op, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {Operator Selection}
\label{tbl:opsel}
\end{table*}

>>>>

\begin{figure*}[t]
<<op.all.3,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
dfd <- subset(df, !(strategy %in% c('op','opsel')) )
ggplot(dfd, aes(sd.reduction, mutant.reduction)) + geom_point(aes(shape=type, color=sqr)) + facet_wrap(~strategy) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
@
\label{fig:fullimgshape}
\end{figure*}
<<opsel>>=
stats.op <- subset(stats.rest, grepl('^(op:|TSDL)', operator))
o.stats.sel.op <- subset(o.f(stats.op), select=sel.colnames)
r.stats.sel.op <- subset(r.f(stats.op), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^(op:|TSDL)', operator))
colnames(o.stats.sel.op) <- new.colnames
colnames(r.stats.sel.op) <- new.colnames

#o.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
#r.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')

@@

#o.stats.sel.one$sampling  <- gsub('_.*','', o.stats.sel.one$operator)
@

<<opselx>>=
stats.opsel <- subset(stats.rest, grepl('^opsel', operator))
o.stats.sel.opsel <- subset(o.f(stats.opsel), select=sel.colnames)
r.stats.sel.opsel <- subset(r.f(stats.opsel), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^opsel', operator))
colnames(o.stats.sel.opsel) <- new.colnames
colnames(r.stats.sel.opsel) <- new.colnames

#o.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
#r.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')

o.stats.sel.opsel$operator  <- gsub('_','',gsub('op.*:','', o.stats.sel.opsel$operator))
r.stats.sel.opsel$operator  <- gsub('_','',gsub('op.*:','', r.stats.sel.opsel$operator))

o.stats.sel.opsel <- o.stats.sel.opsel[,c(1,7,2,3,4,5,6)]
r.stats.sel.opsel <- r.stats.sel.opsel[,c(1,7,2,3,4,5,6)]

#o.stats.sel.one$sampling  <- gsub('_.*','', o.stats.sel.one$operator)
@

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.op, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.op, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {Operators}
\label{tbl:operators}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.opsel, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.opsel, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {Operator Selection}
\label{tbl:opsel}
\end{table*}
